---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shrtcts

<!-- badges: start -->
<!-- badges: end -->

**shrtcts** lets you make anything an RStudio shortcut!

## Installation

You can install the `shrtcts` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("gadenbuie/shrtcts")
```

## Quick Intro

Store your shortcuts in `~/.config/.shrtcts.yaml` or `~/.shrtcts.yaml`.
Each shortcut should look something like the example below,
but you can include _any R code you want_ as the shortcut `Binding`.

```yaml
- Name: Say Something Nice
  Description: A demo of cool things
  Binding: praise::praise
  Interactive: true
```

Then add this to your `~/.Rprofile` 
(use `usethis::edit_r_profile()` to find this file quickly).

```{r eval=FALSE}
if (interactive() & requireNamespace("shrtcts", quietly = TRUE)) {
  shrtcts::add_rstudio_shortcuts()
}
```

After restarting  your R session, 
you'll find your new shortcut
**Say Something Nice**
in your RStudio Addins menu!

## Details

```{r child="man/fragments/shrtcts-yaml-format.Rmd"}
```

```{r child="man/fragments/rstudio-keyboard-shortcuts.Rmd"}
```
